---
title: "KmerFrequencyBoxplot"
author: "Uma Arora"
date: "3/18/2020"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)

```


```{r pressure, echo=FALSE}
setwd('/Users/arorau/Desktop/Dumont_Lab/k-merDigging/centromere_kmers/copynumber/k31_GCcorrection/data/')
k31 <- read.table(file = 'final.set1.k31.correctedcount.txt', header = TRUE)
#remove no PCR libraries
k31 <- k31[k31$LIBRARY != 'P2 NO PCR', ]
k31 <- k31[k31$LIBRARY != 'SLX500HC', ]
k31 <- k31[k31$LIBRARY != 'NO PCR', ]
k31Musmusculus <- k31[k31$TAXONOMY == 'Mus musculus',]
k31Musmusculusconsensus <- k31Musmusculus[k31Musmusculus$CON.SCR == 'CONSENSUS',]
k31MusmusculusconsensusMINOR <- k31Musmusculusconsensus[k31Musmusculusconsensus$SAT=='MINOR',]
k31MusmusculusconsensusMAJOR <- k31Musmusculusconsensus[k31Musmusculusconsensus$SAT=='MAJOR',]

#Reorder strains
k31Musmusculusconsensus$STRAIN = factor(k31Musmusculusconsensus$STRAIN,levels(k31Musmusculusconsensus$STRAIN)[c(26,10,3,8,6,1,12,4,25,2,5,9,11,14,16,17,18,19,20,21,22,23,15,24)])

svg(filename = 'GCcorr_Mmusculus_InbredandWild_Con_minorandmajor_k31.svg', 
    width = 16, 
    height = 9)


ggplot(k31Musmusculusconsensus, aes(x = STRAIN, y= CORRECTEDCOUNT, fill = SAT)) + 
  geom_boxplot() +
  facet_grid(cols = vars(k31Musmusculusconsensus$POPULATION), scales = "free_x")+
  theme_bw() + 
  theme_light() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=15),
        axis.title = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(size=20,face="bold") ) +
  xlab("Mus musculus Inbred Strains") +
  ylab("Log10(GC-corrected k-mer frequency)") +
  labs(fill="Major/Minor") 

dev.off()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Is the data normally distributed?
Density plot
Minor satellite
```{r}
plot(density(k31MusmusculusconsensusMINOR$CORRECTEDCOUNT),
     main = "Density plot of GC-corrected minor satellite 31-mer frequency")

```
Density plot
Major satellite
```{r}
plot(density(k31MusmusculusconsensusMAJOR$CORRECTEDCOUNT),
     main = "Density plot of GC-corrected minor satellite 31-mer frequency")
```



Q-Q plot

```{r}
qqnorm(k31MusmusculusconsensusMINOR$CORRECTEDCOUNT)
qqline(k31MusmusculusconsensusMINOR$CORRECTEDCOUNT, col = 2)
```

```{r}
qqnorm(k31MusmusculusconsensusMAJOR$CORRECTEDCOUNT)
qqline(k31MusmusculusconsensusMAJOR$CORRECTEDCOUNT, col = 2)
```


Statistical tests
Calculating within strain variance and between strain variance with the Kruskal Wallis test
calculate differences for major and minor satellite separately




Calculate strain differences using an ANOVA
MINOR
```{r}
k31MusmusculusconsensusMINOR_AOV <- aov(CORRECTEDCOUNT ~ STRAIN, data = k31MusmusculusconsensusMINOR)
summary(k31MusmusculusconsensusMINOR_AOV)
tuk_k31MusmusculusconsensusMINOR_AOV <- TukeyHSD(k31MusmusculusconsensusMINOR_AOV)
tuk_k31MusmusculusconsensusMINOR_AOV
```

MAJOR
```{r}
k31MusmusculusconsensusMAJOR_AOV <- aov(CORRECTEDCOUNT ~ STRAIN, data = k31MusmusculusconsensusMAJOR)
summary(k31MusmusculusconsensusMAJOR_AOV)
tuk_k31MusmusculusconsensusMAJOR_AOV <- TukeyHSD(k31MusmusculusconsensusMAJOR_AOV)
tuk_k31MusmusculusconsensusMAJOR_AOV
```

Inbred strain differences

Calculate strain differences using an ANOVA
MINOR
```{r}
k31MusmusculusconsensusMINORinbred <- k31MusmusculusconsensusMINOR[k31MusmusculusconsensusMINOR$POPULATION == "Inbred",]

k31MusmusculusconsensusMINORinbred_AOV <- aov(CORRECTEDCOUNT ~ STRAIN, data = k31MusmusculusconsensusMINORinbred)
summary(k31MusmusculusconsensusMINORinbred_AOV)
tuk_k31MusmusculusconsensusMINORinbred_AOV <- TukeyHSD(k31MusmusculusconsensusMINORinbred_AOV)
tuk_k31MusmusculusconsensusMINORinbred_AOV
```

MAJOR
```{r}
k31MusmusculusconsensusMAJORinbred <- k31MusmusculusconsensusMAJOR[k31MusmusculusconsensusMAJOR$POPULATION == "Inbred",]

k31MusmusculusconsensusMAJORinbred_AOV <- aov(CORRECTEDCOUNT ~ STRAIN, data = k31MusmusculusconsensusMAJORinbred)
summary(k31MusmusculusconsensusMAJORinbred_AOV)
tuk_k31MusmusculusconsensusMAJORinbred_AOV <- TukeyHSD(k31MusmusculusconsensusMAJORinbred_AOV)
tuk_k31MusmusculusconsensusMAJORinbred_AOV
```

t-test btw inbred strains and wild mice 
k31Musmusculusconsensus
```{r}

k31Musmusculusconsensus_inbredwildAOV <- aov(CORRECTEDCOUNT ~ POPULATION, data = k31Musmusculusconsensus)
summary(k31Musmusculusconsensus_inbredwildAOV)


t.test(k31Musmusculusconsensus$CORRECTEDCOUNT~k31Musmusculusconsensus$POPULATION)

```


