---
title: "SupFigure1"
author: "Uma Arora"
date: "11/2/2020"
output: html_document
---


```{r setup, include=FALSE}
library(dplyr)
library(corrplot)
```

Exclude No PCR libraries
129P2 NO PCR
129P2 500 HC
129S5 NO PCR

```{r}
k31set1 <- read.table(file = 'final.set1.k31.correctedcount.txt', header = TRUE)

k31set1 <- k31set1[k31set1$LIBRARY != 'P2 NO PCR', ]
k31set1 <- k31set1[k31set1$LIBRARY != 'SLX500HC', ]
k31set1 <- k31set1[k31set1$LIBRARY != 'NO PCR', ]

```



```{r cars}

corrplotdf <- data.frame(KMER = factor(),
                         CORRECTEDCOUNT = numeric())



for (i in levels(k31set1$LIBRARY)){
  lib <- k31set1[k31set1$LIBRARY == i,]
  lib <- lib[,c(1,12)]
  colnames(lib) <- c("KMER", i)
  corrplotdf <- merge(lib, corrplotdf, by = "KMER", all = TRUE)
}

```



```{r}

#Remove caroli, pahari, wild spret, inbred spret
corrplotdfMusmus <- corrplotdf[,-c(1,9,10,11,12,13,14,15,16,27,37,86,87,88,89,90,91,92,93,95,97,99,103,104,105,106,107,108,109,110,111,112,113,120)]

#Remove no PCR libraries
corrplotdfMusmus <- corrplotdfMusmus[,-c(8,13,14)]

corrplotdfMusmus <- na.omit(corrplotdfMusmus)

##Reorder rows
#with excluding no pcr libraries
corrplotdfMusmusreorder <- corrplotdfMusmus[,c(12,83,20,25,8,9,23,29,10,11,78,14,15,21,19,26,17,24,22,30,16,28,13,18,27,1,2,3,4,5,6,7,31,32,33,34,35,36,50,51,60,61,70,71,79,80,81,82,37,38,39,52,53,54,55,56,57,58,59,62,63,64,65,66,67,68,69,72,73,74,75,76,77,40,41,42,43,44,45,46,47,48,49)]

##Calculate correlations
N <- cor(corrplotdfMusmusreorder)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

svg(filename = 'corrplot_allstrains_library.svg', 
    width = 15, 
    height = 15)

corrplot(N, 
         type = "upper")

dev.off()

```

Plots with only inbred strains

```{r}
#without noPCR
corrplotdfMusmusreorderINBRED <- corrplotdfMusmusreorder[,1:25]

N2 <- cor(corrplotdfMusmusreorderINBRED)

svg(filename = 'corrplot_inbredstrains_GCnorm_library.svg', 
    width = 6, 
    height = 6)

corrplot(N2, 
         type = "upper",
         cl.lim=c(0,1)) 

         
dev.off()



```

Statistics: Rho, p-value

Between libraries

	Between libraries
CAST/EiJ	0.9989764
129S5SvEvBrd	0.9930516
	0.9932797
	0.9949828
C57BL/6NJ	0.999004
129P2/OlaHsd	0.9863634 #no PCR
	0.9921627 #no pcr
	0.9959852 #no pcr
	0.9933695
	0.9876263 #no pcr
	0.9961487#no pcr
A/J	0.9968131
	0.9980495
	0.9984989
WSB/EiJ	0.9993602
129S1/SvImJ	0.9997391
C3H/HeJ	0.999662
DBA/2J	0.9989149
PWK/PhJ	0.9902781

1. CAST/EiJ libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$LB4505650,corrplotdfMusmusreorderINBRED$LB3888061)
```

2. 129S5SvEvBrd libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$SLX500DSS,corrplotdfMusmusreorderINBRED$SLX300DSS)

```
3. C57BL/6NJ libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$LB4505614,corrplotdfMusmusreorderINBRED$LB3888056)
```
4. 129P2/OlaHsd libraries
```{r}

cor.test(corrplotdfMusmusreorderINBRED$`P2 SLX500DSS`,corrplotdfMusmusreorderINBRED$`P2 SLX300DSS`)

```
5. A/J libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$LB7469040,corrplotdfMusmusreorderINBRED$LB5442420)
cor.test(corrplotdfMusmusreorderINBRED$LB7469040,corrplotdfMusmusreorderINBRED$LB4505627)
cor.test(corrplotdfMusmusreorderINBRED$LB5442420,corrplotdfMusmusreorderINBRED$LB4505627)
```
6. WSB/EiJ libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$LB4505662,corrplotdfMusmusreorderINBRED$LB3888060)
```

7. 129S1/SvImJ libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$LB4505687,corrplotdfMusmusreorderINBRED$LB3888089)
```
7. C3H/HeJ libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$LB4505626,corrplotdfMusmusreorderINBRED$LB3888055)
```
8. DBA/2J libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$LB4505698,corrplotdfMusmusreorderINBRED$LB3888057)
```
9. PWK/PhJ libraries
```{r}
cor.test(corrplotdfMusmusreorderINBRED$LB4505686,corrplotdfMusmusreorderINBRED$LB3888058)
```

```{r}
libraries <- c(0.9989764,0.9930516,0.9932797,0.9949828,0.999004,0.9863634,0.9921627,0.9959852,0.9933695,0.9876263,0.9961487,0.9968131,0.9980495,0.9984989,0.9993602,0.9997391,0.999662,0.9989149,0.9902781)
libraries <- as.data.frame(libraries)
zalende <- as.data.frame(N2[-1,1])
colnames(zalende) <- c("corr")
fvb <-  as.data.frame(N2[-c(1:2),2])
colnames(fvb) <- c("corr")
cast1 <- as.data.frame(N2[-c(1:3),3])
colnames(cast1) <- c("corr")
cast2 <- as.data.frame(N2[-c(1:4),4])
colnames(cast2) <- c("corr")
S51 <- as.data.frame(N2[-c(1:5),5])
colnames(S51) <- c("corr")
s52 <- as.data.frame(N2[-c(1:6),6])
colnames(s52) <- c("corr")
b6n1 <- as.data.frame(N2[-c(1:7),7])
colnames(b6n1) <- c("corr")
b6n2 <- as.data.frame(N2[-c(1:8),8])
colnames(b6n2) <- c("corr")
p21 <- as.data.frame(N2[-c(1:9),9])
colnames(p21) <- c("corr")
p22 <- as.data.frame(N2[-c(1:10),10])
colnames(p22) <- c("corr")
molf <- as.data.frame(N2[-c(1:11),11])
colnames(molf) <- c("corr")
aj1 <- as.data.frame(N2[-c(1:12),12])
colnames(aj1) <- c("corr")
aj2 <- as.data.frame(N2[-c(1:13),13])
colnames(aj2) <- c("corr")
aj3 <- as.data.frame(N2[-c(1:14),14])
colnames(aj3) <- c("corr")
wsb1 <- as.data.frame(N2[-c(1:15),15])
colnames(wsb1) <- c("corr")
wsb2 <- as.data.frame(N2[-c(1:16),16])
colnames(wsb2) <- c("corr")
s11 <- as.data.frame(N2[-c(1:17),17])
colnames(s11) <- c("corr")
s12 <- as.data.frame(N2[-c(1:18),18])
colnames(s12) <- c("corr")
c3h1 <- as.data.frame(N2[-c(1:19),19])
colnames(c3h1) <- c("corr")
c3h2 <- as.data.frame(N2[-c(1:20),20])
colnames(c3h2) <- c("corr")
d21 <- as.data.frame(N2[-c(1:21),21])
colnames(d21) <- c("corr")
d22 <- as.data.frame(N2[-c(1:22),22])
colnames(d22) <- c("corr")
lewes <- as.data.frame(N2[-c(1:23),23])
colnames(lewes) <- c("corr")
pwk1 <- as.data.frame(N2[-c(1:24),24])
colnames(pwk1) <- c("corr")


strains <- rbind(zalende,fvb,cast1,cast2,S51,s52,b6n1,b6n2,p21,p22,molf,aj1,aj2,aj3,wsb1,wsb2,s11,s12,c3h1,c3h2,d21,d22,lewes,pwk1)

mean(libraries$libraries)
#[1] 0.9953824

t.test(strains,libraries)
```

